Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-04 Experiments.tex
Small changes in the text

Comments to address in this section:
\begin{enumerate}
    \item REVIEWER 2: In the weak scalability evaluations (in Figure 7 and
    8), the overhead of the Next Generation Executor (NGE) has grown linearly
    with the number of the nodes. Can you explain why the average time
    execution time of AthenaMP is decreased even when the overhead is
    increasing?
\end{enumerate}

@@

We observe that, despite some fluctuations due to external factors (e.g.,
Titan's shared filesystem and the shared database used by the NGE), the
average execution time of AthenaMP ranges between 4200 and 4800 seconds. We
also observe that in all the cases the gap between AthenaMP execution times
and the pilot durations is minimal, although it slightly increases with the
pilot size. We notice that NGE's overhead does grow linearly with the number
of units.

>>>>

Comments to address in this section:
\begin{enumerate}
    \item REVIEWER 2: In the weak scalability evaluations (in Figure 7 and
    8), the overhead of the Next Generation Executor (NGE) has grown linearly
    with the number of the nodes. Can you explain why the average time
    execution time of AthenaMP is decreased even when the overhead is
    increasing?
    I checked the data. Figure 8 was simply wrong. I think that we have overwritten the original with an older version.  Figure 7: I used a smaller integration step to compute the integral of the pilot concurrency. It gets better but not as much as I would like. Our data has something sketchy.  
\end{enumerate}

@@

We observe that, despite some fluctuations due to external factors (e.g.,
Titan's shared filesystem and the shared database used by the NGE), the
average execution time of AthenaMP ranges between 4500 and 4800 seconds. We
also observe that in all the cases the gap between AthenaMP execution times
and the pilot durations is minimal, although it slightly increases with the
pilot size. We notice that NGE's overhead does grow linearly with the number
of units.
